---
title: "Mapping of city locations"
author: "James Wellnitz"
date: "March 27, 2019"
output:
  html_document: default
  pdf_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

Cord data set is generated from a gis hookup to locate cites. The look up is not 100% accurate as only city and state name are given
This notebook goes through the prosess of cleaing up the cordinate point and plotting the accurate one on a map to give a general idea of distribution

read in data
```{r}
cords <- read.csv("C:/Users/still/OneDrive/Purdue S4/STAT 355/Cord.csv")
```

remove NA values and convert to SpatialPoints
```{r}
library(sp)
cords <- cords[!is.na(cords$lat),]
cords.vector <- cbind(cords$long, cords$lat)
cords.sp <- SpatialPoints(cords.vector, proj4string = CRS("+proj=longlat"))
```

create SPatialPolygon map of US
```{r echo=FALSE}
library(maps)
library(rgeos)
library(maptools)
usa <- map('state', fill = TRUE)
usa <- map2SpatialPolygons(usa, IDs = usa$names, proj4string = CRS("+proj=longlat"))
```

remove points outside US
```{r}
cords.over <- over(cords.sp, usa, returnList = TRUE)
cords.over <- cords[!is.na(cords.over == 0),]
```

plot
```{r echo = FALSE}
library(ggplot2)
ggplot(usa, aes(x=long, y=lat, group=group)) + geom_polygon(fill="white", color="black") +xlim(c(-130,-67))+ ylim(c(25,50)) + geom_point(data = cords.over, inherit.aes = F, aes(x=long, y=lat), color="red", alpha=.8)
```

